---
name: Samuel
surname: Langton
position: "Postdoc researcher"
address: "De Boelelaan 1077, 1081HV, Amsterdam"
www: www.samlangton.info
email: "slangton@nscr.nl"
twitter: sh_langton
github: langtonhugh
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
headcolor: 080007
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD Sociology", "2016-2021", "Manchester Metropolitan University (UK)", "Fully-funded Vice-Chancellor’s doctoral scholarship",
  "MSc Sociology and Social Research", "2014-2016", "Utrecht University (NL)", "Full-time research masters",
  "BSc Social Policy with Government", "2009-2012", "London School of Economics (UK)", "Awarded 2.1"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Research employment

```{r}
packages_used <- tibble::tribble(
  ~ pos, ~ date, ~ instit, ~ details,
  # nscr
  "Postdoc Researcher", "2021-now", "Netherlands Institute for the Study of Crime and Law Enforcement (NL)", c("Evidence-based policing research group", "Emergency demand for police services", "Systematic literature review"),
  # leeds
  "Research Fellow", "2020-2021", "University of Leeds (UK)", "COVID19 and crime",
  # mmupostdoc
  "Research Associate", "2019-2020", "Manchester Metropolitan University (UK)", c("Police demand", "Violence Reduction Unit"),
  # mmura
  "Research Assistant", "2016-2018", "Manchester Metropolitan University (UK)", c("Police demand", "Mental ill-health")
)
packages_used %>%
  detailed_entries(what = pos, when = date, with = instit, why = details)

```

```{r, eval = F}
tribble(
  ~Year, ~Pos, ~Desc, ~Extra,
  "2021-now", "Postdoc Researcher"  , "Netherlands Institute for the Study of Crime and Law Enforcment", "blah blah blah",
  "2020-2021", "Research Fellow", "University of Leeds", "blah blah blah",
  "2019-2020", "Research Associate", "Manchester Metropolitan Crime and Well-being Big Data Centre", "blah blah blah",
  "2016-2018", "Research Assistant", "Manchester Metropolitan Crime and Well-being Big Data Centre", "blah blah blah"
) %>%
  brief_entries(
    what = Pos,
    when = Year,
    with = Desc,
    why = Extra
  )
```

# Peer-reviewed journal articles

```{r}
library(dplyr)
# knitr::write_bib("papers.bib")

bibliography_entries("papers.bib")
```

# Books & book chapters

```{r}
# library(dplyr)
# knitr::write_bib("papers.bib")

bibliography_entries("books.bib")
```

# Other publications

# Invited presentations

# Presentations

# Teaching

# Reviewer

Journal article reviewer for _Crime Science_, _Police Practice and Research_, _Applied Geography_, _Environment and Planning B: Urban Analytics and City Science_, _Urban Design International_, and _Journal of Housing and the Built Environment_.

# Other employment

# Software experience


