%% Template for a CV
%% Author: Rob J Hyndman

\documentclass[10pt,a4paper,]{article}
\usepackage[scaled=0.86]{DejaVuSansMono}
\usepackage[sfdefault,lf,t]{carlito}

% Change color to blue
\usepackage{color,xcolor}
\definecolor{headcolor}{HTML}{171817}

\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true,hidelinks]{hyperref}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{geometry}
\geometry{left=1.75cm,right=1.75cm,top=2.2cm,bottom=2cm}

\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother



\date{december 2023}


\usepackage{paralist,ragged2e,datetime}
\usepackage[hyphens]{url}
\usepackage{fancyhdr,enumitem,pifont}
\usepackage[compact,small,sf,bf]{titlesec}

\RaggedRight
\sloppy

% Header and footer
\pagestyle{fancy}
\makeatletter
\lhead{\sf\textcolor[gray]{0.4}{Curriculum Vitae: \@name}}
\rhead{\sf\textcolor[gray]{0.4}{\thepage}}
\cfoot{}
\def\headrule{{\color[gray]{0.4}\hrule\@height\headrulewidth\@width\headwidth \vskip-\headrulewidth}}
\makeatother

% Header box
\usepackage{tabularx}

\makeatletter
\def\name#1{\def\@name{#1}}
\def\info#1{\def\@info{#1}}
\makeatother
\newcommand{\shadebox}[3][.9]{\fcolorbox[gray]{0}{#1}{\parbox{#2}{#3}}}

\usepackage{calc}
\newlength{\headerboxwidth}
\setlength{\headerboxwidth}{\textwidth}
%\addtolength{\headerboxwidth}{0.2cm}
\makeatletter
\def\maketitle{
\thispagestyle{plain}
\vspace*{-1.4cm}
\shadebox[0.9]{\headerboxwidth}{\sf\color{headcolor}\hfil
\hbox to 0.98\textwidth{\begin{tabular}{l}
\\[-0.3cm]
\LARGE\textbf{\@name}
\\[0.1cm]\large Postdoc researcher\\[0.6cm]
\normalsize\textbf{Curriculum Vitae}\\
\normalsize december 2023
\end{tabular}
\hfill\hbox{\fontsize{9}{12}\sf
\begin{tabular}{@{}rl@{}}
\@info
\end{tabular}}}\hfil
}
\vspace*{0.2cm}}
\makeatother

% Section headings
\titlelabel{}
\titlespacing{\section}{0pt}{1.5ex}{0.5ex}
\titleformat*{\section}{\color{headcolor}\large\sf\bfseries}
\titleformat*{\subsection}{\color{headcolor}\sf\bfseries}
\titlespacing{\subsection}{0pt}{1ex}{0.5ex}

% Miscellaneous dimensions
\setlength{\parskip}{0ex}
\setlength{\parindent}{0em}
\setlength{\headheight}{15pt}
\setlength{\tabcolsep}{0.15cm}
\clubpenalty = 10000
\widowpenalty = 10000
\setlist{itemsep=1pt}
\setdescription{labelwidth=1.2cm,leftmargin=1.5cm,labelindent=1.5cm,font=\rm}

% Make nicer bullets
\renewcommand{\labelitemi}{\ding{228}}

\usepackage{booktabs,fontawesome5}
%\usepackage[t1,scale=0.86]{sourcecodepro}

\name{Samuel Langton}
\def\imagetop#1{\vtop{\null\hbox{#1}}}
\info{%
 %
\faIcon{home} & \href{http://www.samlangton.info}{www.samlangton.info}\\% %
%
%
\faIcon{envelope} & \href{mailto:slangton@nscr.nl}{\nolinkurl{slangton@nscr.nl}}\\%
\faIcon{twitter} & \href{https://twitter.com/sh\_langton}{@sh\_langton}\\%
\faIcon{github} & \href{https://github.com/langtonhugh}{langtonhugh}\\%
%
%
%
%
}


%\usepackage{inconsolata}


\setlength\LTleft{0pt}
\setlength\LTright{0pt}

% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}


\def\endfirstpage{\newpage}

\begin{document}
\maketitle


\hypertarget{education}{%
\section{Education}\label{education}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2016-2020 & \parbox[t]{0.85\textwidth}{%
\textbf{PhD Criminology}\\[-0.1cm]{\footnotesize Manchester Metropolitan University, Manchester, UK.}}\\[0.4cm]
2014-2016 & \parbox[t]{0.85\textwidth}{%
\textbf{MSc Sociology and Social Research}\\[-0.1cm]{\footnotesize Utrecht University, Utrecht, Netherlands.}}\\[0.4cm]
2009-2012 & \parbox[t]{0.85\textwidth}{%
\textbf{BSc Social Policy with Government}\\[-0.1cm]{\footnotesize London School of Economics, London, UK.}}\\[0.4cm]
\end{longtable}

\hypertarget{research-employment}{%
\section{Research employment}\label{research-employment}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2021-now & \parbox[t]{0.85\textwidth}{%
\textbf{Postdoc Researcher}\\[-0.1cm]{\footnotesize Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.}}\\[0.4cm]
2020-2021 & \parbox[t]{0.85\textwidth}{%
\textbf{Research Fellow}\\[-0.1cm]{\footnotesize University of Leeds, Leeds, UK.}}\\[0.4cm]
2019-2020 & \parbox[t]{0.85\textwidth}{%
\textbf{Research Associate}\\[-0.1cm]{\footnotesize Manchester Metropolitan University, Manchester, UK.}}\\[0.4cm]
2017-2018 & \parbox[t]{0.85\textwidth}{%
\textbf{Research Assistant (part-time)}\\[-0.1cm]{\footnotesize Manchester Metropolitan University, Manchester, UK.}}\\[0.4cm]
\end{longtable}

\hypertarget{visiting-positions}{%
\section{Visiting positions}\label{visiting-positions}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2020-now & \parbox[t]{0.85\textwidth}{%
\textbf{Visiting Research Fellow}\\[-0.1cm]{\footnotesize Policy Evaluation and Research Unit, Manchester Metropolitan University, Manchester, UK.}}\\[0.4cm]
\end{longtable}

\hypertarget{peer-reviewed-journal-articles}{%
\section{Peer-reviewed journal
articles}\label{peer-reviewed-journal-articles}}

\emph{If you do not have free access to any of these articles, please
email me and I will send you a copy.} \linebreak

\hypertarget{refs-018106d21508b671268fb512e33aaec1}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-langton2023amsterdam}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Langton, S., Verlaan, T., \& Ruiter, S. (2023).
Operationalizing deployment time in police calls for service.
\emph{Crime Science}.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2022demand}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Langton, S., Ruiter, S., \& Verlaan, T. (2022).
Describing the scale and composition of calls for police service: A
replication and extension using open data. \emph{Police Practice and
Research}.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2021policing}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Langton, S., Bannister, J., Ellison, M., Haleem, M. S.,
\& Krzemieniewska-Nandwani, K. (2021). Policing and mental ill-health:
Using big data to assess the scale and severity of, and the frontline
resources committed to, mental ill-health-related calls-for-service.
\emph{Policing: A Journal of Policy and Practice}, \emph{15}(3),
1963--1976.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2021cartograms}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Langton, S., \& Solymosi, R. (2021). Cartograms,
hexograms and regular grids: Minimising misrepresentation in spatial
data visualisations. \emph{Environment and Planning B: Urban Analytics
and City Science}, \emph{48}(2), 348--357.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2021small}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Langton, S., Dixon, A., \& Farrell, G. (2021). Small
area variation in crime effects of COVID-19 policies in England and
Wales. \emph{Journal of Criminal Justice}, \emph{75}, 101830.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2021six}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Langton, S., Dixon, A., \& Farrell, G. (2021). Six
months in: pandemic crime trends in England and Wales. \emph{Crime
Science}, \emph{10}(1), 1--16.}

\leavevmode\vadjust pre{\hypertarget{ref-buil2021accuracy}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Buil-Gil, D., Moretti, A., \& Langton, S. (2021). The
accuracy of crime statistics: Assessing the impact of police data bias
on geographic crime analysis. \emph{Journal of Experimental
Criminology}, 1--27.}

\leavevmode\vadjust pre{\hypertarget{ref-adepeju2021anchored}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Adepeju, M., Langton, S., \& Bannister, J. (2021).
Anchored k-medoids: A novel adaptation of k-medoids further refined to
measure long-term instability in the exposure to crime. \emph{Journal of
Computational Social Science}, \emph{4}(2), 655--680.}

\leavevmode\vadjust pre{\hypertarget{ref-adepeju2020akmedoids}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Adepeju, M., Langton, S., \& Bannister, J. (2020).
Akmedoids R package for generating directionally-homogeneous clusters of
longitudinal data sets. \emph{Journal of Open Source Software},
\emph{5}(56), 2379--2379.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2017residential}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Langton, S., \& Steenbeek, W. (2017). Residential
burglary target selection: An analysis at the property-level using
Google Street View. \emph{Applied Geography}, \emph{86}, 292--299.}

\end{CSLReferences}

\hypertarget{books-book-chapters}{%
\section{Books \& book chapters}\label{books-book-chapters}}

\hypertarget{refs-43bb75d62a426e63f146b3c7247610e1}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-verlaan2023data}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Verlaan, T., \& Langton, S. (2023). On the use of
inferential statistics on administrative police data. In L. Huey \& D.
Buil-Gil (Eds.), \emph{The crime data handbook}. Bristol: Policy Press.}

\leavevmode\vadjust pre{\hypertarget{ref-langton2020open}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Langton, S., \& Solymosi, R. (2023). Open street map for
crime and place. In E. Groff \& C. Haberman (Eds.), \emph{Understanding
crime and place: A methods handbook}. Temple University Press.}

\leavevmode\vadjust pre{\hypertarget{ref-wooditch2021beginner}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Wooditch, A., Johnson, N. J., Solymosi, R., Medina, J.
J., \& Langton, S. (2021). \emph{A Beginner's Guide to Statistics for
Criminology and Criminal Justice Using R}. Springer.}

\leavevmode\vadjust pre{\hypertarget{ref-buil2020gis}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Buil-Gil, D., \& Langton, S. (2020). GIS and geovisual
analysis. In P. Atkinson, S. Delamont, A. Cernat, J. W. Sakshaug, \& R.
A. Williams (Eds.), \emph{SAGE research methods foundations}. Sage
Publications Ltd.}

\end{CSLReferences}

\hypertarget{preregistrations}{%
\section{Preregistrations}\label{preregistrations}}

\hypertarget{refs-ce11f0318060747a43ec297f7d71c55d}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-barsprereg}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Langton, S., Ruiter, S., Connolly, A., \& Menges, V.
(2023). \emph{The spatio-temporal relationship between bars and
violence.} \url{https://osf.io/ex7ga.}}

\leavevmode\vadjust pre{\hypertarget{ref-demandpreg}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Langton, S., Verlaan, T., \& Ruiter, S. (2022).
\emph{Scale and composition of emergency reactive police demand in
Amsterdam, Netherlands.} \url{https://osf.io/qgwv6/.}}

\leavevmode\vadjust pre{\hypertarget{ref-scopingprereg}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Langton, S., Ruiter, S., \& Schoonmade, L. (2021).
\emph{Protocol -- A systematic scoping review on the spatial and
temporal patterning of emergency demand for police services.}
\url{https://osf.io/qwrb3/.}}

\end{CSLReferences}

\hypertarget{other-publications}{%
\section{Other publications}\label{other-publications}}

\hypertarget{refs-acd3d2f20247c35a4e4afc08d3e11a95}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-policinginsight}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Farrell, G., Langton, S., \& Dixon, A. (2020). \emph{Six
months in: Pandemic crime trends in England and Wales to August 2020}.
\url{https://policinginsight.com/features/analysis/six-months-in-pandemic-crime-trends-in-england-and-wales-to-august-2020/.}}

\leavevmode\vadjust pre{\hypertarget{ref-leeds}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Langton, S. (2020). \emph{Crime and Anti-social
behaviour in Greater London}.
\url{https://covid19-crime.com/wp-content/uploads/sites/92/2020/07/COVIDCrimeStatsBulletin_3_Langton_GtrLondonCrime-3.pdf.}}

\leavevmode\vadjust pre{\hypertarget{ref-convo1}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Langton, S. (2020). \emph{Lockdown crime trends: Why
antisocial behaviour is up.}
\url{https://theconversation.com/lockdown-crime-trends-why-antisocial-behaviour-is-up-140479.}}

\leavevmode\vadjust pre{\hypertarget{ref-convo2}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Langton, S. (2019). \emph{Even the most beautiful maps
can be misleading.}
\url{https://theconversation.com/even-the-most-beautiful-maps-can-be-misleading-126474.}}

\leavevmode\vadjust pre{\hypertarget{ref-convo3}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Langton, S. (2017). \emph{When crime drops, the demands
on the police don't necessarily fall.}
\url{https://theconversation.com/when-crime-drops-the-demands-on-the-police-dont-necessarily-fall-79288.}}

\end{CSLReferences}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2023 & \parbox[t]{0.85\textwidth}{%
\textbf{The spatio-temporal relationship between bars and violence}\\[-0.1cm]{\footnotesize Environmental Criminology and Crime Analysis, Stockholm, Sweden.}}\\[0.4cm]
2022 & \parbox[t]{0.85\textwidth}{%
\textbf{Demand for emergency police services in the Netherlands}\\[-0.1cm]{\footnotesize Environmental Criminology and Crime Analysis, Harrogate, UK.}}\\[0.4cm]
2022 & \parbox[t]{0.85\textwidth}{%
\textbf{Demand for emergency (police) services in the Netherlands using open data}\\[-0.1cm]{\footnotesize Nederlandse Vereniging voor Criminologie, Leiden, Netherlands.}}\\[0.4cm]
2021 & \parbox[t]{0.85\textwidth}{%
\textbf{Police demand and supply in the Netherlands: an evidence-based approach of police deployment}\\[-0.1cm]{\footnotesize Onderzoek bij, voor en door de Politie (online).}}\\[0.4cm]
2021 & \parbox[t]{0.85\textwidth}{%
\textbf{Demand for emergency (police) services in the Netherlands using open data}\\[-0.1cm]{\footnotesize European Society of Criminology conference (online).}}\\[0.4cm]
2021 & \parbox[t]{0.85\textwidth}{%
\textbf{Open Science for Crime and Open Science for Crime and
Policing Research}\\[-0.1cm]{\footnotesize University of Manchester seminar on bias in police records (online).}}\\[0.4cm]
2020 & \parbox[t]{0.85\textwidth}{%
\textbf{Six Months In: Pandemic Crime Trends in England and Wales}\\[-0.1cm]{\footnotesize COVID-19 and crime research seminar, hosted by University of Leeds and University College London (online).}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Demonstrating the theoretical and empirical distinctions between offenders and crimes}\\[-0.1cm]{\footnotesize European Society of Criminology conference, Ghent, Belgium.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Improving interpretation through cartograms, hexograms and regular grids}\\[-0.1cm]{\footnotesize GISRUK annual proceedings, Newcastle, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Offender residential concentrations: a longitudinal study in the United Kingdom}\\[-0.1cm]{\footnotesize European Society of Criminology conference, Sarajevo, Bosnia and Herzegovina.}}\\[0.4cm]
2018 & \parbox[t]{0.85\textwidth}{%
\textbf{Rapid change in ethnic composition – part of a wider Brexit picture?}\\[-0.1cm]{\footnotesize GISRUK annual proceedings, Leicester, UK.}}\\[0.4cm]
2017 & \parbox[t]{0.85\textwidth}{%
\textbf{Neighbourhood trajectories: a longitudinal study of offender residence concentrations}\\[-0.1cm]{\footnotesize European Society of Criminology conference, Cardiff, UK.}}\\[0.4cm]
2016 & \parbox[t]{0.85\textwidth}{%
\textbf{Residential burglary target selection: an analysis at the property-level using Google Street View}\\[-0.1cm]{\footnotesize Postgrad session at Spatial Behaviour and Crime symposium, Royal Netherlands Academy of Sciences, Amsterdam, Netherlands.}}\\[0.4cm]
\end{longtable}

\newpage

\hypertarget{invited-presentations}{%
\section{Invited presentations}\label{invited-presentations}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2023 & \parbox[t]{0.85\textwidth}{%
\textbf{Demand for police in the Netherlands}\\[-0.1cm]{\footnotesize The Hague regional police force, the Netherlands.}}\\[0.4cm]
2022 & \parbox[t]{0.85\textwidth}{%
\textbf{How decisions about spatial data visualisation affect map legibility}\\[-0.1cm]{\footnotesize Ministry of Defence, UK (online).}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{The geography of offender housing in Birmingham}\\[-0.1cm]{\footnotesize West Midlands Police HQ, Birmingham, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Visualising geographic information: examining methods of improving the thematic map}\\[-0.1cm]{\footnotesize Quantitative Spatial Science Group, School of Geographical Sciences, University of Bristol, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Visualising and explaining small area offender trajectories in Birmingham, England}\\[-0.1cm]{\footnotesize Centre for Criminology and Criminal Justice, University of Manchester, Manchester, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Visualising geographic information: examining methods of improving the thematic map}\\[-0.1cm]{\footnotesize Open Data Manchester, Manchester, UK.}}\\[0.4cm]
\end{longtable}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2021-now & \parbox[t]{0.85\textwidth}{%
\textbf{Instructor and co-organiser, internal R workshops \& Data Carpentry sessions}\\[-0.1cm]{\footnotesize Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.}}\\[0.4cm]
2020 & \parbox[t]{0.85\textwidth}{%
\textbf{Lead instructor, A gentle introduction to QGIS}\\[-0.1cm]{\footnotesize Open Data Manchester webinar series (online).}}\\[0.4cm]
2020 & \parbox[t]{0.85\textwidth}{%
\textbf{Lead instructor, Introduction to QGIS}\\[-0.1cm]{\footnotesize Cathie Marsh Institute for Social Research, University of Manchester, Manchester, UK.}}\\[0.4cm]
2020 & \parbox[t]{0.85\textwidth}{%
\textbf{Lead instructor, Data visualisation in R using crime data}\\[-0.1cm]{\footnotesize UK Data Service and Cathie Marsh Institute for Social Research, University of Manchester, Manchester, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Lead instructor, R for police forces}\\[-0.1cm]{\footnotesize West Midlands Police HQ, Birmingham, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Instructor and co-organiser, Intro to R for criminologists}\\[-0.1cm]{\footnotesize European Society of Criminology conference, Ghent, Belgium.}}\\[0.4cm]
2018-2020 & \parbox[t]{0.85\textwidth}{%
\textbf{Co-instructor, Getting started in R: an introduction to data analysis and visualisation}\\[-0.1cm]{\footnotesize Methods@Manchester Summer School, University of Manchester, Manchester, UK.}}\\[0.4cm]
2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Instructor, Introduction to cluster analysis using R}\\[-0.1cm]{\footnotesize Cathie Marsh Institute for Social Research, University of Manchester,  Manchester, UK.}}\\[0.4cm]
2018 & \parbox[t]{0.85\textwidth}{%
\textbf{Instructor qualification}\\[-0.1cm]{\footnotesize Data and Software Carpentry}}\\[0.4cm]
2018 & \parbox[t]{0.85\textwidth}{%
\textbf{Lead instructor, Introduction to R}\\[-0.1cm]{\footnotesize Researcher Development Programme for Postgrads and Staff, Manchester Metropolitan University, Manchester, UK.}}\\[0.4cm]
\end{longtable}

\hypertarget{supervision}{%
\section{Supervision}\label{supervision}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2023-now & \parbox[t]{0.85\textwidth}{%
\textbf{Natascha de Leeuw doctoral thesis (caretaker), Van aangifte tot opheldering en vervolging}\\[-0.1cm]{\footnotesize Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.}}\\[0.4cm]
2021-now & \parbox[t]{0.85\textwidth}{%
\textbf{Tim Verlaan doctoral thesis, Demand and supply for policing in the Netherlands}\\[-0.1cm]{\footnotesize Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.}}\\[0.4cm]
2022-2023 & \parbox[t]{0.85\textwidth}{%
\textbf{Aisling Connolly research internship, Temporal analysis of risky facilities and police demand}\\[-0.1cm]{\footnotesize Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.}}\\[0.4cm]
\end{longtable}

\hypertarget{reviewer}{%
\section{Reviewer}\label{reviewer}}

Peer-reviewed papers for \emph{European Journal of Criminology},
\emph{Crime Science}, \emph{Police Practice and Research}, \emph{Applied
Geography}, \emph{Environment and Planning B: Urban Analytics and City
Science}, \emph{Journal of Housing and the Built Environment},
\emph{International Criminal Justice Review}, and the UK Home Office.

\hypertarget{other-employment}{%
\section{Other employment}\label{other-employment}}

\begin{longtable}{@{\extracolsep{\fill}}ll}
2017-2019 & \parbox[t]{0.85\textwidth}{%
\textbf{Freelance data analyst and author}\\[-0.1cm]{\footnotesize Policing Insight website (remote).}}\\[0.4cm]
2015-2016 & \parbox[t]{0.85\textwidth}{%
\textbf{Teaching and student assistant}\\[-0.1cm]{\footnotesize Department of Sociology, Utrecht University, Utrecht, Netherlands}}\\[0.4cm]
2012-2014 & \parbox[t]{0.85\textwidth}{%
\textbf{Insolvency administrator and trainee accountant}\\[-0.1cm]{\footnotesize Accura Accountants, London, UK.}}\\[0.4cm]
\end{longtable}

\hypertarget{software-experience}{%
\section{Software experience}\label{software-experience}}

R/RStudio, QGIS, Atlas.ti, GeoDa.

\hypertarget{languages}{%
\section{Languages}\label{languages}}

English (native), Dutch (A2-B1).

\hypertarget{other-interests}{%
\section{Other interests}\label{other-interests}}

Running, outdoor swimming, freediving, playing bass guitar and learning
piano.

\end{document}
