---
name: Samuel
surname: Langton
position: "Postdoc researcher"
# address: "De Boelelaan 1077, 1081HV, Amsterdam"
www: www.samlangton.info
email: "slangton@nscr.nl"
twitter: sh_langton
github: langtonhugh
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
headcolor: 171817
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(dplyr)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, #~ add,
  "PhD Sociology", "2016-2020", "Manchester Metropolitan University, Manchester, UK.",
  "MSc Sociology and Social Research", "2014-2016", "Utrecht University, Utrecht, Netherlands.",
  "BSc Social Policy with Government", "2009-2012", "London School of Economics, London, UK.",
) %>% 
  brief_entries(what = Degree, when = Year, with = Institution)
```

# Research employment

```{r}
research_emp <- tribble(
  ~ pos, ~ date, ~ instit, #~ details,
  # nscr
  "Postdoc Researcher", "2021-now", "Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.",
  # c("Evidence-based policing research group",
  #   "Examining emergency demand for police",
  #   ""),
  # leeds
  "Research Fellow", "2020-2021", "University of Leeds, Leeds, UK.",
  # "COVID-19 and crime project",
  # mmupostdoc
  "Research Associate", "2019-2020", "Manchester Metropolitan University, Manchester, UK.",
  # c("Violence Reduction Unit project"),
  # mmura
  "Research Assistant (part-time)", "2017-2018", "Manchester Metropolitan University, Manchester, UK."
)

research_emp %>%
  brief_entries(what = pos, when = date, with = instit) # , why = details

```

# Visiting positions

```{r}
research_pos <- tribble(
  ~ pos, ~ date, ~ instit, #~ details,
  # peru
  "Visiting Research Fellow", "2020-now", "Policy Evaluation and Research Unit, Manchester Metropolitan University, Manchester, UK.",
)

research_pos %>%
  brief_entries(what = pos, when = date, with = instit) # , why = details
```

# Peer-reviewed journal articles

_If you do not have free access to any of these articles, please email me and I will send you a copy._ \linebreak

```{r}
# knitr::write_bib("papers.bib")

bibliography_entries("papers.bib", )
```

# Books & book chapters

```{r}
# library(dplyr)
# knitr::write_bib("papers.bib")

bibliography_entries("books.bib")
```

# Preregistrations

```{r}
# library(dplyr)
# knitr::write_bib("papers.bib")

bibliography_entries("prereg.bib")
```

# Other publications

```{r}
# library(dplyr)
# knitr::write_bib("papers.bib")

bibliography_entries("others.bib")
```

# Presentations

```{r}
tribble(
  ~ date, ~ title, ~ where,
  "2022", "Demand for emergency police services in the Netherlands", "Environmental Criminology and Crime Analysis, Harrogate, UK.",
  "2022", "Demand for emergency (police) services in the Netherlands using open data", "Nederlandse Vereniging voor Criminologie, Leiden, Netherlands.",
  "2021", "Police demand and supply in the Netherlands: an evidence-based approach of police deployment", "Onderzoek bij, voor en door de Politie (online).",
  "2021", "Demand for emergency (police) services in the Netherlands using open data", "European Society of Criminology conference (online).",
    "2021", "Open Science for Crime and Open Science for Crime and
Policing Research", "University of Manchester seminar on bias in police records (online).",
  "2020", "Six Months In: Pandemic Crime Trends in England and Wales", "COVID-19 and crime research seminar, hosted by University of Leeds and University College London (online).",
  "2019", "Demonstrating the theoretical and empirical distinctions between offenders and crimes", "European Society of Criminology conference, Ghent, Belgium.",
  "2019", "Improving interpretation through cartograms, hexograms and regular grids", "GISRUK annual proceedings, Newcastle, UK.",
  "2019", "Offender residential concentrations: a longitudinal study in the United Kingdom", "European Society of Criminology conference, Sarajevo, Bosnia and Herzegovina.",
  "2018", "Rapid change in ethnic composition – part of a wider Brexit picture?", "GISRUK annual proceedings, Leicester, UK.",
  "2017", "Neighbourhood trajectories: a longitudinal study of offender residence concentrations", "European Society of Criminology conference, Cardiff, UK.",
  "2016", "Residential burglary target selection: an analysis at the property-level using Google Street View", "Postgrad session at Spatial Behaviour and Crime symposium, Royal Netherlands Academy of Sciences, Amsterdam, Netherlands."
) %>% 
  brief_entries(title, date, where)
```

# Invited presentations

```{r}
tribble(
  ~ date, ~ title, ~ where,
  # mod
  "2022", "How decisions about spatial data visualisation affect map legibility", "Ministry of Defence, UK (online).",  
  # wmp
  "2019", "The geography of offender housing in Birmingham", "West Midlands Police HQ, Birmingham, UK.",  
  # bristol
  "2019", "Visualising geographic information: examining methods of improving the thematic map", "Quantitative Spatial Science Group, School of Geographical Sciences, University of Bristol, UK.",  
  # manc
  "2019", "Visualising and explaining small area offender trajectories in Birmingham, England", "Centre for Criminology and Criminal Justice, University of Manchester, Manchester, UK.",  
  # open data manc
  "2019", "Visualising geographic information: examining methods of improving the thematic map", "Open Data Manchester, Manchester, UK.",  
) %>% 
  brief_entries(title, date, where)
```

# Teaching

```{r}
tribble(
  ~ date, ~ job, ~ details,
  "2021-now", "Instructor and co-organiser, NSC-R workshop series", "Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.",
  "2020", "Lead instructor, A gentle introduction to QGIS", "Open Data Manchester webinar series (online).",
  "2020", "Lead instructor, Introduction to QGIS", "Cathie Marsh Institute for Social Research, University of Manchester, Manchester, UK.",
  "2020", "Lead instructor, Data visualisation in R using crime data", "UK Data Service and Cathie Marsh Institute for Social Research, University of Manchester, Manchester, UK.",
  "2019", "Lead instructor, R for police forces", "West Midlands Police HQ, Birmingham, UK.",
  "2019", "Instructor and co-organiser, Intro to R for criminologists", "European Society of Criminology conference, Ghent, Belgium.",
  "2018-2020", "Co-instructor, Getting started in R: an introduction to data analysis and visualisation", "Methods@Manchester Summer School, University of Manchester, Manchester, UK.",
  "2019", "Instructor, Introduction to cluster analysis using R", "Cathie Marsh Institute for Social Research, University of Manchester,  Manchester, UK.",
  "2018", "Instructor qualification", "Data and Software Carpentry",
  "2018", "Lead instructor, Introduction to R", "Researcher Development Programme for Postgrads and Staff, Manchester Metropolitan University, Manchester, UK."
) %>% 
  brief_entries(job, date, details)
```

# Supervision

```{r}
tribble(
  ~ date, ~ job, ~ details,
  "2021-now", "Tim Verlaan doctoral thesis, Demand and supply for policing in the Netherlands", "Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands.",
    "2022-now", "Aisling Connolly research internship, Temporal analysis of risky facilities and police demand", "Netherlands Institute for the Study of Crime and Law Enforcement, Amsterdam, Netherlands."
) %>% 
  brief_entries(job, date, details)
```

# Reviewer

Journal article reviewer for _Crime Science_, _Police Practice and Research_, _Applied Geography_, _Environment and Planning B: Urban Analytics and City Science_, _Urban Design International_, and _Journal of Housing and the Built Environment_.

# Other employment

```{r}
tribble(
  ~ date, ~ job, ~ details,
  "2017-2019", "Freelance data analyst and author", "Policing Insight website (remote).",
  "2015-2016", "Teaching and student assistant", "Department of Sociology, Utrecht University, Utrecht, Netherlands",
  "2012-2014", "Insolvency administrator and trainee accountant", "Accura Accountants, London, UK."
) %>% 
  brief_entries(job, date, details)
```

# Software experience

R/RStudio, QGIS, GeoDa, Atlas.ti.

# Other interests

Cycling, jogging, outdoor swimming, freediving, playing bass guitar and learning piano.
